---
title: "OptumDay4DS"
output: html_document
date: "2023-06-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
ohtani_batted_balls <-
    read_csv("https://shorturl.at/mnwL1")
head(ohtani_batted_balls)
```
#Visualizing 1Dcategoricaldata
```{r}
ohtani_batted_balls %>%
ggplot(aes(x = batted_ball_type)) +
geom_bar() +
theme_bw()
```
#Marginal distribution:
```{r}
ohtani_batted_balls %>%
ggplot(aes(x = batted_ball_type)) +
geom_bar(aes(y = after_stat(count) / sum(af
theme_bw()
```
#Computeanddisplaytheproportionsdirectly
```{r}
ohtani_batted_balls %>%
group_by(batted_ball_type) %>%
summarize(count = n()) %>%
ungroup() %>%
mutate(total = sum(count),
prop = count / total) %>%
ggplot(aes(x = batted_ball_type)) +
geom_bar(aes(y = prop),
stat = "identity") +
theme_bw()
```
#confidence internvals
```{r}
ohtani_batted_balls %>%
    group_by(batted_ball_type) %>%
    summarize(count = n()) %>%
    ungroup() %>%
    mutate(total = sum(count),
        prop = count / total,
        se = sqrt(prop * (1 - prop) / total),
        lower = prop - 2 * se,
        upper = prop + 2 * se) %>%
    ggplot(aes(x = batted_ball_type)) +
    geom_bar(aes(y = prop),
        stat = "identity") +
    geom_errorbar(aes(ymin = lower,
        ymax = upper),
        color = "red") +
    theme_bw()
```
#forcats 
```{r}
ohtani_batted_balls %>%
    group_by(batted_ball_type) %>%
    summarize(count = n()) %>%
    ungroup() %>%
    mutate(total = sum(count),
        prop = count / total,
        se = sqrt(prop * (1 - prop) / total),
        lower = prop - 2 * se,
        upper = prop + 2 * se,
        batted_ball_type =
        fct_reorder(batted_ball_type,
            prop)) %>%
    ggplot(aes(x = batted_ball_type)) +
    geom_bar(aes(y = prop),
        stat = "identity") +
    geom_errorbar(aes(ymin = lower,
        ymax = upper),
        color = "red") +
    theme_bw()
```
#Describing 1Dcontinuousdata
```{r}
summary(ohtani_batted_balls$exit_velocity)
```
#Box plotsvisualizesummarystatistics
```{r}
ohtani_batted_balls %>%
    ggplot(aes(y = exit_velocity)) +
    geom_boxplot(aes(x = "")) +
    theme_bw() +
    coord_flip()
```
#Histogramsdisplay 1Dcontinuousdistributions

```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity)) +
    geom_histogram() +
    theme_bw()
```

#Displaythedatapointsdirectly withbeeswarm plots
```{r}
install.packages('ggbeeswarm')
library(ggbeeswarm)
ohtani_batted_balls %>%
    ggplot(aes(y = exit_velocity)) +
    geom_beeswarm(aes(x = ""),
        cex = 3) +
    theme_bw() +
    coord_flip()
```

#Smoothsummary withviolinplots
```{r}
ohtani_batted_balls %>%
    ggplot(aes(y = exit_velocity)) +
    geom_violin(aes(x = "")) +
    theme_bw() +
    coord_flip()
```

#Smoothsummary withviolinplots + box plots
```{r}
ohtani_batted_balls %>%
    ggplot(aes(y = exit_velocity,
        x = "")) +
    geom_violin() +
    geom_boxplot(width = .2) +
    theme_bw() +
    coord_flip()
```
#Displayfulldistribution withECDFplot
```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity)) +
    stat_ecdf() +
    theme_bw()
```

#Rugplotsdisplayraw data
```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity)) +
    geom_rug(alpha = 0.7) +
    theme_bw()
```

#Rugplotssupplementotherdisplays
```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity)) +
    geom_rug(alpha = 0.7) +
    geom_histogram() +
    theme_bw()
```
```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity)) +
    geom_rug(alpha = 0.7) +
    stat_ecdf() +
    theme_bw()
```
#Scatterplotsfor 2Dcontinuousdata
```{r}
ohtani_batted_balls %>%
    ggplot(aes(x = exit_velocity,
        y = launch_angle)) +
    geom_point() +
    geom_rug(alpha = 0.4) +
    theme_bw()
```

