---
title: "DSlecture5"
output: html_document
date: "2023-06-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#create dataset
```{r}

library(tidyverse)
ohtani_batted_balls <- read_csv("https://shorturl.at/mnwL1")
head(ohtani_batted_balls)
```
#Variables of interest: pitch_type and batted_ball_type - but how many levels does pitch_type have?
```{r}
table(ohtani_batted_balls$pitch_type)
```
#We can manually fct_recode pitch_type (see Chapter 15 of R for Data Science for more on factors)
```{r}
ohtani_batted_balls <- ohtani_batted_balls %>%
  filter(pitch_type != "null") %>%
  mutate(pitch_type = fct_recode( pitch_type,
      "Changeup" = "CH"
      ,
      "Breaking ball" = "CU"
      ,
      "Fastball" = "FC"
      ,
      "Fastball" = "FF"
      ,
      "Fastball" = "FS"
      ,
      "Breaking ball" = "KC"
      ,
      "Fastball" = "SI"
      ,
      "Breaking ball" = "SL"))
```

#Inferencefor categoricaldata
```{r}
chisq.test(table(ohtani_batted_balls$pitch_type))
```
#2DCategoricalvisualization(== morebar charts!)
#stacked
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = batted_ball_type,
            fill = pitch_type)) +
  geom_bar() + theme_bw()
```

#side by side 
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = batted_ball_type,
              fill = pitch_type)) +
  geom_bar(position = "dodge") + theme_bw()
```

#Stacked bar charts emphasize marginal distribution of x variable,
#Side-by-side bar charts are useful to show the conditional distribution of fill variable given x,

#Review of joint, marginal,andconditionalprobabilities
```{r}
proportions(table(ohtani_batted_balls$pitch_type, ohtani_batted_balls$batted_ball_type))
```

#BONUS: pivot_wider example
```{r}
install.packages('gt')
require(plyr)
require(dplyr)
library(gt)
ohtani_batted_balls %>%
  group_by(batted_ball_type, pitch_type) %>%
  summarize(joint_prob = n() / nrow(ohtani_batted_balls)) %>%
  pivot_wider(names_from = batted_ball_type, values_from = joint_prob,
              values_fill = 0)
```

#Inferencefor 2Dcategoricaldata
```{r}
chisq.test(table(ohtani_batted_balls$pitch_type, ohtani_batted_balls$batted_ball_type))
```
#Create a mosaic plot using base R
```{r}
mosaicplot(table(ohtani_batted_balls$pitch_type, ohtani_batted_balls$batted_ball_type),
shade = TRUE, main = "Relationship between batted ball and pitch type?")
```

#Continuousbycategorical:side-by-sideandcolor
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = pitch_type,
            y = exit_velocity)) +
  geom_violin() +
  geom_boxplot(width = .2) +
  theme_bw()
```


```{r}

```
#Whatabout forhistograms?
```{r}
ohtani_batted_balls %>%
ggplot(aes(x = exit_velocity,
          fill = pitch_type)) +
geom_histogram() +
theme_bw() + theme(legend.position = "botto")
```

```{r}
ohtani_batted_balls %>%
ggplot(aes(x = exit_velocity,
          fill = pitch_type)) +
geom_histogram(alpha = .25, position = "ideal"
theme_bw() + theme(legend.position = "botto"))
```

#Wecanalwaysfacet instead...
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = exit_velocity)) +
  geom_histogram() +
  theme_bw() +
  facet_wrap(~ pitch_type, ncol = 2)
```
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = exit_velocity)) +
  geom_histogram() +
  theme_bw() +
  facet_grid(pitch_type ~., margins = TRUE)
```
#Facets makeiteasyto movebeyond 2D
```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = pitch_type,
              fill = batted_ball_type)) +
  geom_bar() + theme_bw() +
  facet_wrap(~ outcome, ncol = 5) +
  theme(legend.position = "bottom")
```

#We make a scatterplot with geom_point()
```{r}
ohtani_batted_balls %>%
ggplot(aes(x = exit_velocity,
            y = launch_angle)) +
geom_point() +
theme_bw()
```


```{r}
ohtani_batted_balls %>%
  ggplot(aes(x = exit_velocity,
              y = launch_angle,
  color = batted_ball_type)) +
  geom_point() +
  theme_bw()
```

